---
title: "Regression"
author: "delpinolisette"
date: "11/26/2020"
output: github_document
---

# Regression 1
 So far, have only really manipulated data and reshaped/recoded variables. The next step is to use this tidied data to perform regression. 

 Linear regression can be thought of predicting one variable using a second variable. 

 ## Exercise 1:

 Try to predict election outcome based on facial appearance (compare election outcomes for a candiate based on 'facial competence' ratings by surveyed students.) Build a linear regression model. 

 ### Step 1

 Decide which is the binary predictor variable and which is the binary outcome variable. 

 ```{r}
 # load in libraries to read csv and then plot using ggplot. 
 library(tidyverse)
 library(ggrepel)

 face_rate<-read_csv("face.csv")

 # take a look at face_rate
 head(face_rate)
 ```

 It looks like the data frame contains `d.comp` and `r.comp` headers. Those record measures of competency based only on brief viewings of the candidate's face. 

 Also, `l.party` tracks the party of the candidate. 

 `r.vote` and `d.vote` track the election outcomes (number of votes) for that particular election. 

 Thus, the independent binary predictor should correspond to the compentency ratings and the binary outcome should predict to whether the candidate won or lost. 

#### Prepping The Outcome Variable:
To prep the outcome variable, calculate the difference in the share of votes between Democratic and Republican candidates. 

why? `r.share` tracks the *proportion* of the vote that the republican candidate won, while `d.share` tracks the *proportion* of the vote that the democratic candidate won.

```{r}
face_rate$r.share<-face_rate$r.votes / (face_rate$r.votes + face_rate$d.votes)
#head(face_rate)

face_rate$d.share<-face_rate$d.votes/(face_rate$r.votes + face_rate$d.votes)
#head(face_rate$d.share)

# margins
face_rate$diff_in_vote_share <-(face_rate$d.share - face_rate$r.share)
head(face_rate$diff_in_vote_share)
```

So now the `diff_in_vote_share` column tracks the differences in vote share. If positive, the democratic candidate got that much more proportional share of the vote. 

## Step 2: Plot the Data Using ggplot for initial guesses

